Data Flow Analysis\\in the Presence of Correlated Calls

### 2014-12-03 content/datastr.tex
started to move proofs to appendix; removing dependency on minted

\newpage    
\begin{lemma}\label{lem:normeq}
    $\denote{\mathcal N(\updfun f^*)}=\denote{\updfun f^*}.$
\end{lemma}

\begin{proof}
    Let $\updfun f^*=\setpair I U$.
    For any $\tau\in T,$
    \[
        \begin{aligned}
            \denote{\mathcal N(\updfun f^*)}(\tau)
            &=\denote{\mathcal N(\langle I,\ U\rangle)}(\tau)\\
            &=\denote{\setpair{I\cup U}U}(\tau)\\
            &=\tau\cap(I\cup U)\cup U\\
            &=(\tau\cap I)\cup(\tau\cap U)\cup U\\
            &=\tau\cap I\cup U\\
            &=\denote{\setpair IU}(\tau)\\
            &=\denote{\updfun f^*}(\tau)\,.
        \end{aligned}
    \]
    Thus, $\denote{\mathcal N(\updfun f^*)}=\denote{\updfun f^*}$.
\end{proof}

@@

\begin{lemma}
    Let $\setpair IU$ and $\setpair{I'}{U'}$ be two normalized update functions such that $\setpair IU\ne\setpair {I'}{U'}$. Then $\denote{\setpair IU}\ne\denote{\setpair {I'}{U'}}$.
\end{lemma}

\begin{proof}
    Let us show that there always exists a set $\tau\subseteq T$ such that $\denote{\setpair IU}(\tau)\ne\denote{\setpair{I'}{U'}}(\tau)$. There are two cases:
    \begin{enumerate}
        \item $U\ne U'$. Then for the empty set $\tau=\varnothing$,
            \[
                \denote{\setpair IU}(\tau)=\denote{\setpair IU}(\varnothing)=(\varnothing\cap I)\cup U=U\,,
            \]
            whereas 
            \[ 
                \denote{\setpair {I'}{U'}}(\tau)=\denote{\setpair {I'}{U'}}(\varnothing)=(\varnothing\cap I')\cup U'=U'.
            \]
            Hence, $\denote{\setpair IU}\ne\denote{\setpair {I'}{U'}}$.
        \item $I\ne I'$. Then for the set of all types $\tau=T$,
            \[
                \denote{\setpair IU}(\tau)=\denote{\setpair IU}(T)=(T\cap I)\cup U=I\cup U\,.
            \]
            Since $\setpair IU$ is normalized, $U\subseteq I$, and
            \[
                I\cup U= I\,.
            \]
            At the same time,
            \[
                \denote{\setpair {I'}{U'}}(\tau)=\denote{\setpair {I'}{U'}}(T)=(T\cap I')\cup U'=I'\cup U'=I'\,.
            \]
            Since $I\ne I'$, it follows that $\denote{\setpair IU}\ne \denote{\setpair {I'}{U'}}$. \qedhere
    \end{enumerate}
\end{proof}

>>>>

\begin{lemma}\label{lem:normeq}
    $\denote{\mathcal N(\updfun f^*)}=\denote{\updfun f^*}.$
\end{lemma}

@@

\begin{lemma}\label{lem:normuneq}
    Let $\setpair IU$ and $\setpair{I'}{U'}$ be two normalized update functions such that $\setpair IU\ne\setpair {I'}{U'}$. Then $\denote{\setpair IU}\ne\denote{\setpair {I'}{U'}}$.
\end{lemma}
